Computer Science House Constitution

### 2022-02-13 constitution.tex
waivers: clarify usage of the process, add dual directorship waiver

\asubsection{Waiving of Requirements}
\begin{enumerate}
  \item The following requirements may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
    \begin{enumerate}
      \item Candidates must have at least one full semester of House membership as an Active Member
      \item Candidates must reside on floor during the term of office
    \end{enumerate}
  \item This process waives the enumerated requirements for a given election for all candidates on a per-directorship basis
\end{enumerate}

>>>>

\asubsection{Waiving of Requirements}
\begin{enumerate}
  \item The following requirements may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
    \begin{enumerate}
      \item Candidates must have at least one full semester of House membership as an Active Member
      \item Candidates must reside on floor during the term of office
      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
    \end{enumerate}
  \item This process operates for one requirement at a time
  \item This process operates for one voting executive board position or the Chairperson at a time
  \item This process operates on the current election only
  \item Any requirements waived using this process are waived for all candidates for the given position for the current election process
\end{enumerate}
